---
title: '**Expected FA contract for 2018**'
author: "Jaehyun Lee"
date: "2018/10/08"
output:
  ioslides_presentation: default
---

## 0. Table of Content

## 1. Data preprocessing
* FA1218B2.csv - Statiz
* FA1218P2.csv - Statiz
```{r, include=FALSE}
Sys.setlocale("LC_ALL", "C")
getwd()
setwd("C:/Users/dlwog/Desktop")
baseball_statcast <- read.csv("FA1218B2.csv", header = TRUE)
```

## 1. Data preprocessing
* Normalization
```{r}
normalize <- function(x) {
  return((x - min(x)) / (max(x) - min(x)))
}

normalize_baseball <- as.data.frame(lapply(baseball_statcast, normalize))
```

## 1. Data preprocessing
* Revert from normalization
```{r}
unnormalize <-  function(x) { 
  return((x * (max(baseball_statcast$aincome) - min(baseball_statcast$aincome))) + min(baseball_statcast$aincome))
}
```

## 1. Data preprocessing
* Data segmentation (train Vs. test)
```{r}
set.seed(1)
strain <- sample(1:nrow(normalize_baseball), 40)
stest <- (-strain)
training <- normalize_baseball[strain,]
test <- normalize_baseball[stest,]
```

## 1. Data preprocessing
* Data segmentation (train Vs. test)
```{r}
summary(training$aincome)
summary(test$aincome)
```

## 2. Create a Neural network model
```{r}
library(neuralnet)
set.seed(1)
baseball_model <-  neuralnet(aincome ~ tWAR + WAR + age + Pscore + G + PA + AB + R + X1B + X2B + X3B + HR + TB + RBI + SB + CS + BB + HBP + IBB + SO + GDP + SH + SF + AVG + OBP + SLG + OPS + wOBA + wRC., data = training, hidden = c(1,1))
```

## 2. Create a Neural network model
* Model evaluation
```{r}
set.seed(1)
model_results <-  compute(baseball_model, test[1:((ncol(test)) - 2)])
predicted_aincome <-  model_results$net.result
```

## 2. Create a Neural network model
* Model evaluation
```{r}
cor(predicted_aincome, test$aincome)
```

## 2. Create a Neural network model
* Model evaluation
```{r}
GS <- unnormalize(test$aincome)
set.seed(1)
NS <- unnormalize(predicted_aincome)
cor(NS,GS)
sqrt(mean(NS - GS)^2)
```

## 3. Create a regression model
```{r}
library(glmnet)
baseball_statcast <- read.csv("FA1218B2.csv", header = TRUE)
x <- model.matrix(aincome ~., baseball_statcast)[,-1]
y <- baseball_statcast$aincome
```

## 3. Create a regression model
* Data segmentation (train Vs. test)
```{r}
set.seed(1)
train = sample(1:nrow(baseball_statcast),40)
test = (-train)
ytest = y[test]
```

## 3. Create a regression model
* Find lambda with minimal MSE (Cross Validation)
```{r}
for (i in 0:10) {
set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.1*i)
lasso.coef = predict(cv.lasso, type = "coefficients", s = cv.lasso$lambda.min)
lasso.prediction = predict(cv.lasso, s = cv.lasso$lambda.min, newx = x[test,])
lasso.coef
cv.lasso$lambda.min
c <- cor(lasso.prediction, ytest)
d <- sqrt((mean(lasso.prediction - ytest)^2))
print(c)
print(d)
print(0.1*i)
}
```

## 3. Create a regression model
* Find lambda with minimal MSE (Cross Validation)
```{r}
set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.3)
plot(cv.lasso$glmnet.fit, xvar="lambda", label=TRUE)
```