---
title: '**Cy young prediction**'
author: "Jaehyun Lee"
date: "2018/09/17"
output:
  ioslides_presentation: default
---

## 1. Data preprocessing
* baseball reference
    * Awards Voting data - cy.csv
    * Player Standard Pitching data - cy2018.csv
    * Player Value data - cy2018.csv
* Lahman
    * pitching data - pitching.csv

```{r, include=FALSE}
setwd("C:\\Users\\dlwog\\Desktop\\Rcode")
library(plyr)
pitching <- read.csv("pitching2017.csv")
cy <- read.csv("Cy.csv")
cy2018 <- read.csv("cy2018.csv")
```

## 1. Data preprocessing
```{r}
cy$Nameco <- as.character(cy$Nameco)
cyy <- cy[,-c(1:6, 8, 9, 13, 34)]
Acy2018 <- subset(cy2018, Lg == "AL")
Ncy2018 <- subset(cy2018, Lg == "NL")
```

## 2. Create a regression model
* Generalized linear model
* Vote points

## 2.1 Train Data, Test Data
```{r}
library(glmnet)
x <- model.matrix(Vote.Pts ~., cyy)[,-1]
y <- cyy$Vote.Pts
set.seed(1)
train = sample(1:nrow(cyy),190)
test = (-train)
ytest = y[test]
```

## 2.2 Model application
```{r}
set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.8)
lasso.coef = predict(cv.lasso, type = "coefficients",
                     s = cv.lasso$lambda.min) # coefficients
lasso.prediction = predict(cv.lasso, s = cv.lasso$lambda.min,
                           newx = x[test,]) # coefficients
```

## 2.2 Model application
```{r}
lasso.coef
b <- lasso.coef
```

## 2.2 Model application
* WAR, W, L, ERA, CG, WHIP

## 2.3 Find the minimum MSE
```{r}
cv.lasso$lambda.min
cor(lasso.prediction, ytest)
sqrt((mean(lasso.prediction - ytest)^2))
```

## 3. Create function
```{r}
cpoint <- function(py) {
  d <- with(py, 
            b[1]
            + b[2] * WAR 
            + b[3] * W + b[4] * L
            + b[5] * ERA + b[7] * GS
            + b[9] * CG + b[10] * SHO
            + b[11] * SV + b[12] * IP
            + b[15] * ER + b[16] * HR
            + b[17] * BB + b[18] * IBB
            + b[19] * SO + b[20] * HBP
            + b[22] * WP + b[24] * WHIP
            )
  d
}
```

## 4. Result
## 4.1 Apply functions to AL
```{r}
Aresult <- cpoint(Acy2018)
head(Acy2018$Name[(order(Aresult, decreasing = T))])
```

## 4.2 Apply functions to NL
```{r}
Nresult <- cpoint(Ncy2018)
head(Ncy2018$Name[(order(Nresult, decreasing = T))])
```

## 5. Conclusion
* AL Cy Young Winner
    * Blake Snell
* NL Cy Young Winner
    * Max Scherzer
    
## 6. Add More ++
```{r, include=FALSE}
setwd("C:\\Users\\dlwog\\Desktop\\Rcode")
MVPB <- read.csv("MVPB.csv")
MVPB2018 <- read.csv("MVPB2018.csv")
MVPP <- read.csv("MVPP.csv")
MVPP2018 <- read.csv("MVPP2018.csv")
```

```{r, include=FALSE}
MVPB$Nameco <- as.character(MVPB$Nameco)
NMVPB <- MVPB[,-c(1:5, 7, 8)]
AMVPB2018 <- subset(MVPB2018, Lg == "AL" & AB >= 150)
NMVPB2018 <- subset(MVPB2018, Lg == "NL" & AB >= 150)

library(glmnet)
x <- model.matrix(Vote.Pts ~., NMVPB)[,-1]
y <- NMVPB$Vote.Pts
set.seed(1)
train = sample(1:nrow(NMVPB), 470)
test = (-train)
ytest = y[test]

set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.9)
lasso.coef = predict(cv.lasso, type = "coefficients",
                     s = cv.lasso$lambda.min) # coefficients
lasso.prediction = predict(cv.lasso, s = cv.lasso$lambda.min,
                           newx = x[test,]) # coefficients

lasso.coef
b <- lasso.coef

cv.lasso$lambda.min
cor(lasso.prediction, ytest)
sqrt((mean(lasso.prediction - ytest)^2))

bmpoint <- function(py) {
  d <- with(py, 
            b[1]
            + b[2] * WAR + b[3] * G
            + b[5] * R + b[7] * HR
            + b[8] * RBI + b[9] * SB
            + b[11] * BA + b[12] * OBP
            )
}
```

```{r}
bmAresult <- bmpoint(AMVPB2018)
head(AMVPB2018$Name[(order(bmAresult, decreasing = T))])

bmNresult <- bmpoint(NMVPB2018)
head(NMVPB2018$Name[(order(bmNresult, decreasing = T))])
```

## 6. Add More ++
```{r, include=FALSE}
MVPP$Nameco <- as.character(MVPP$Nameco)
NMVPP <- MVPP[,-c(1:5, 7, 8)]
AMVPP2018 <- subset(MVPP2018, Lg == "AL" & IP >= 50)
NMVPP2018 <- subset(MVPP2018, Lg == "NL" & IP >= 50)

library(glmnet)
x <- model.matrix(Vote.Pts ~., NMVPP)[,-1]
y <- NMVPP$Vote.Pts
set.seed(1)
train = sample(1:nrow(NMVPP), 110)
test = (-train)
ytest = y[test]

set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.9)
lasso.coef = predict(cv.lasso, type = "coefficients",
                     s = cv.lasso$lambda.min) # coefficients
lasso.prediction = predict(cv.lasso, s = cv.lasso$lambda.min,
                           newx = x[test,]) # coefficients

lasso.coef
b <- lasso.coef

cv.lasso$lambda.min
cor(lasso.prediction, ytest)
sqrt((mean(lasso.prediction - ytest)^2))

pmpoint <- function(py) {
  d <- with(py, 
            b[1]
            + b[2] * WAR + b[3] * W + b[4] * L
            + b[5] * ERA + b[6] * WHIP
            + b[7] * G + b[8] * GS
            + b[9] * SV + b[10] * IP
            + b[11] * H
            + b[12] * HR
            + b[13] * BB
            + b[14] * SO
            )
}
```

```{r}
pmAresult <- pmpoint(AMVPP2018)
head(AMVPP2018$Name[(order(pmAresult, decreasing = T))])

pmNresult <- pmpoint(NMVPP2018)
head(NMVPP2018$Name[(order(pmNresult, decreasing = T))])
```

## 6. Add More ++
```{r}
sale <- pmpoint(subset(AMVPP2018, Nameco == "salech01"))
betts <- bmpoint(subset(AMVPB2018, Nameco == "bettsmo01"))
scherzer <- pmpoint(subset(NMVPP2018, Nameco == "scherma01"))
yelich <- bmpoint(subset(NMVPB2018, Nameco == "yelicch01"))
```

## 6. Add More ++
```{r}
betts
sale

yelich
scherzer
```

## 6. Add More ++
* AL MVP Winner
    * Mookie Betts
* NL MVP Winner
    * Christian Yelich
    
# Thank you for watching