---
title: "<font color = ##008B8B>Expected FA contract for 2019</font>"
author: "<font color = ##008B8B>Jaehyun Lee</font>"
date: "<font color = ##008B8B>2018-12-13</font>"
output:
  ioslides_presentation
widescreen : TRUE
---

## <font color = ##008B8B>0. Table of Content</font>
1. Data preprocessing
2. LASSO
3. Create a regression model
4. Applying the model
5. Conclusion

# <font color = ##008B8B>Data preprocessing</font>

## <font color = ##008B8B>1. Data preprocessing</font>

## <font color = ##008B8B>1. Data preprocessing</font>

<center>
<img src = "C:\\Users\\dlwog\\Desktop\\fa1.jpg", width = 65%>
</center>
<center>
<font size="2em">[그림 1: NC 다이노스 양의지]</font>
</center>

## <font color = ##008B8B>1. Data preprocessing</font>

## <font color = ##008B8B>1. Data preprocessing</font>

* Statiz (www.statiz.co.kr)
    * baseball_B - FA1218B1.csv
    * baseball_B2 - FA1218B2.csv
    * baseball_B3 - FA1218P2.csv
    * baseball_P - FA1218P1.csv
    * baseball_P2 - FA1218P2.csv
    * baseball_P3 - FA1218P3.csv

```{r, include=FALSE}
Sys.setlocale("LC_ALL", "C")
getwd()
setwd("C:/Users/dlwog/Desktop")
baseball_B3 <- read.csv("FA1218B3.csv", header = TRUE)
baseball_P3 <- read.csv("FA1218P3.csv", header = TRUE)
baseball_B2 <- read.csv("FA1218B2.csv", header = TRUE)
baseball_P2 <- read.csv("FA1218P2.csv", header = TRUE)
baseball_B1 <- read.csv("FA1218B1.csv", header = TRUE)
baseball_P1 <- read.csv("FA1218P1.csv", header = TRUE)
```

# <font color = ##008B8B>LASSO</font>

## <font color = ##008B8B>2. LASSO</font>

## <font color = ##008B8B>2. LASSO</font>

**LASSO?**

## <font color = ##008B8B>2. LASSO</font>

**LASSO?**

- Associated with linear regression

## <font color = ##008B8B>2. LASSO</font>

**LASSO?**

- Associated with linear regression

- One type of machine learning algorithm

## <font color = ##008B8B>2. LASSO</font>

**LASSO?**

- Associated with linear regression

- One type of machine learning algorithm

- Penalization

# <font color = ##008B8B>Create a regression model</font>

## <font color = ##008B8B>3. Create a regression model</font>

## <font color = ##008B8B>3. Create a regression model</font>

```{r}
library(glmnet)
baseball_B2 <- read.csv("FA1218B2.csv", header = TRUE)
x <- model.matrix(aincome ~., baseball_B2)[,-1]
y <- baseball_B2$aincome
```

## <font color = ##008B8B>3. Create a regression model</font>

**Data segmentation (train Vs. test)**

```{r}
set.seed(1)
train = sample(1:nrow(baseball_B2),40)
test = (-train)
ytest = y[test]
```

## <font color = ##008B8B>3. Create a regression model</font>

**Find lambda with minimal MSE (Cross Validation)**

```{r, eval = FALSE}
for (i in 0:10) {
set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.1*i)
lasso.coef = predict(cv.lasso, type = "coefficients", 
                     s = cv.lasso$lambda.min)
lasso.prediction = predict(cv.lasso, s = cv.lasso$lambda.min,
                           newx = x[test,])
lasso.coef
cv.lasso$lambda.min
c <- cor(lasso.prediction, ytest)
d <- sqrt((mean(lasso.prediction - ytest)^2))
print(c)
print(d)
print(0.1*i)
}
```

## <font color = ##008B8B>3. Create a regression model</font>

**Find lambda with minimal MSE (Cross Validation)**

```{r, echo = FALSE}
for (i in 0:10) {
set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.1*i)
lasso.coef = predict(cv.lasso, type = "coefficients", 
                     s = cv.lasso$lambda.min)
lasso.prediction = predict(cv.lasso, s = cv.lasso$lambda.min,
                           newx = x[test,])
lasso.coef
cv.lasso$lambda.min
c <- cor(lasso.prediction, ytest)
d <- sqrt((mean(lasso.prediction - ytest)^2))
print(c)
print(d)
print(0.1*i)
}
```

## <font color = ##008B8B>3. Create a regression model</font>

**Find lambda with minimal MSE (Cross Validation)**

```{r}
set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.4)
plot(cv.lasso$glmnet.fit, xvar = "lambda", label=TRUE)
```

```{r, echo = FALSE}
baseball_P2 <- read.csv("FA1218P2.csv", header = TRUE)
x <- model.matrix(aincome ~., baseball_P2)[,-1]
y <- baseball_P2$aincome

set.seed(1)
train = sample(1:nrow(baseball_P2), 20)
test = (-train)
ytest = y[test]

set.seed(1)
cv.lasso2 <- cv.glmnet(x[train,], y[train], alpha = 1)
lasso.prediction2 = predict(cv.lasso2, s = cv.lasso2$lambda.min,
                           newx = x[test,])
```
```{r, echo = FALSE}
cv.lasso2$lambda.min
cor(lasso.prediction2, ytest)
sqrt((mean(lasso.prediction2 - ytest)^2))
```

## <font color = ##008B8B>3. Create a regression model</font>

**Create function (B)**

```{r, echo = FALSE}
b = predict(cv.lasso, type = "coefficients", 
                     s = cv.lasso$lambda.min)
b
```

## <font color = ##008B8B>3. Create a regression model</font>

**Create function (B)**

```{r, include = FALSE}
b = predict(cv.lasso, type = "coefficients", 
                     s = cv.lasso$lambda.min)
```
```{r}
FAB <- function(FA) {
  d <- with(FA, 
            b[1]
            + b[2] * tWAR + b[3] * WAR
            + b[4] * age + b[5] * Pscore
            + b[6] * G + b[9] * R
            + b[10] * X1B + b[11] * X2B
            + b[12] * X3B
            + b[13] * HR
            + b[14] * TB
            + b[16] * SB
            + b[18] * BB + b[19] * HBP 
            + b[20] * IBB + b[21] * SO
            + b[22] * GDP + b[24] * SF
            + b[26] * OBP
            )
}
```

## <font color = ##008B8B>3. Create a regression model</font>

**Pitcher model, contract period..**

```{r, include = FALSE}
b2 = predict(cv.lasso2, type = "coefficients", 
                     s = cv.lasso2$lambda.min)
```
```{r, include = FALSE}
FAP <- function(FA) {
  d <- with(FA, 
            b2[1]
            + b2[3] * WAR + b2[4] * age + b2[9] * W
            )
}
```

# <font color = ##008B8B>Applying the model</font>

## <font color = ##008B8B>4. Applying the model</font>

## <font color = ##008B8B>4. Applying the model</font>

```{r}
as.character(baseball_B1[,1])
FABat <- FAB(baseball_B1)
FABat
```

## <font color = ##008B8B>4. Applying the model</font>

```{r}
as.character(baseball_P1[,1])
FAPit <- FAP(baseball_P1)
FAPit
```

## <font color = ##008B8B>4. Applying the model</font>

```{r, echo = FALSE}
library(glmnet)
baseball_B3 <- read.csv("FA1218B3.csv", header = TRUE)
x <- model.matrix(period ~., baseball_B3)[,-1]
y <- baseball_B3$period

set.seed(1)
train = sample(1:nrow(baseball_B3),40)
test = (-train)
ytest = y[test]


set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0.4)
b = predict(cv.lasso, type = "coefficients", 
                     s = cv.lasso$lambda.min)

FAB2 <- function(FA) {
  d <- with(FA, 
            b[1]
            + b[3] * WAR + b[4] * age + b[5] * Pscore
            + b[7] * PA + b[12] * X3B
            + b[17] * CS + b[18] * BB
            + b[25] * AVG
            )
}
```
```{r}
as.character(baseball_B1[,1])
FABat2 <- FAB2(baseball_B1)
FABat2
```

## <font color = ##008B8B>4. Applying the model</font>

```{r, echo = FALSE}
library(glmnet)
baseball_P3 <- read.csv("FA1218P3.csv", header = TRUE)
x <- model.matrix(period ~., baseball_P3)[,-1]
y <- baseball_P3$period

set.seed(1)
train = sample(1:nrow(baseball_P3),20)
test = (-train)
ytest = y[test]

set.seed(1)
cv.lasso <- cv.glmnet(x[train,], y[train], alpha = 0)
b = predict(cv.lasso, type = "coefficients", 
                     s = cv.lasso$lambda.min)

FAP2 <- function(FA) {
  d <- with(FA, b[1] + tWAR * b[2] + WAR * b[3] + age * b[4] + G * b[5] + CG * b[6] + SHO * b[7] + SP * b[8] + W * b[9] + L * b[10] + S * b[11] + H * b[12] + IP * b[13] + R * b[14] + ER * b[15] + PA * b[16] + X1B * b[17] + X2B * b[18] + X3B * b[19] + HR * b[20] + BB * b[21] + IBB * b[22] + HBP * b[23] + SO * b[24] + BK * b[25] + WP * b[26] + ERA * b[27] + FIP * b[28] + WHIP * b[29] + ERA. * b[30] + FIP. * b[31]
  )
}
```
```{r}
as.character(baseball_P1[,1])
FAPit2 <- FAP2(baseball_P1)
FAPit2
```

# <font color = ##008B8B>Conclusion</font>

## <font color = ##008B8B>5. Conclusion</font>

## <font color = ##008B8B>5. Conclusion</font>

```{r}
as.character(baseball_B1[,1])
round(FABat2)
FABat * round(FABat2)
```

## <font color = ##008B8B>5. Conclusion</font>

```{r}
as.character(baseball_P1[,1])
FAPit2 <- FAP2(baseball_P1)
round(FAPit2)
FAPit * round(FAPit2)
```

## <font color = ##008B8B>5. Conclusion</font>

**Reality vs Expectation**

## <font color = ##008B8B>5. Conclusion</font>

**Reality vs Expectation**

- 양의지 [4년 125억원 vs 4년 93억원]

- 모창민 [3년 20억원 vs 3년 17억원]

- 최정 [6년 106억원 vs 4년 94억원]

- 이재원 [4년 69억원 vs 4년 58억원]

# <font color = ##008B8B>Thank you for watching</font>
